% Thesis Acknowledgements ------------------------------------------------


%\begin{acknowledgementslong} %uncommenting this line, gives a different acknowledgements heading
\begin{acknowledgements}      % this creates the heading for the acknowledgments

I would like to thank my supervisor, Prof. Neil Lawrence, for his patient and encouraging guidance, his advice on all aspects of academic life and his constant stream of ideas while allowing me my own mode of work.
For all the effort he put in guaranteeing us, his students, the smoothest of transitions during his promotion and our move to Sheffield.

I would like to thank Michalis Titsias, Kevin Sharp and Mauricio Alvarez for helpful discussions and technical guidance during my one year in Manchester.
The same thanks go to Magnus Rattray, Marta Milo, James Hensman, Nicholas Durrande, Nicolo Fusi and Jaakko Peltonen during my other two years in Sheffield.
I also want to thank Diego di Bernardo for his useful feedback on the experimental data of Chapter \ref{chap2:GP} and John Lafferty for the technical material that sparked the ideas in Chapter \ref{chap6:BiGLasso}.

I had the pleasure of working in two wonderful environments thanks to the staff and head of the MLO group, Prof. Jonathan Shapiro, as well as the staff and director of SITraN, Prof. Pamela Shaw.

For reasons I don't have to mention, I thank colleagues and friends from both labs (alphabetically): Ricardo Andrade, Richard Allmendinger, Mauricio Alvarez, Arjun Chandra, Andreas Damianou, Nicholas Durrande, Nicolo Fusi, Peter Glaus, James Hensman, Antti Honkela, Ciira Maina, Jens Nielsen, Jaakko Peltonen, Adam Pocock, Arif Rahman, Jon Roberts, Kevin Sharp, Manuela Zanda and not least, Michalis Titsias.

Finally, I would like to thank the Engineering and Physical Sciences Research Council for providing the funding which allowed me to undertake this research, and together with the PASCAL Network of Excellence enabled me to attend conferences, workshops and summer schools.

I dedicate this thesis to my grandfather and my late grandmother for giving me the opportunity to pursue my dream. To Laura, for proofreading my meaningless drafts and sitting through my talk rehearsals. I cherish your never-ending support, encouragement and patience. To my brother Kostis, for choosing to move his life to Sheffield and, in the process, being family in proximity; a rare privilege for any foreign student.
      
      

\end{acknowledgements}
%\end{acknowledgmentslong}

% ------------------------------------------------------------------------

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../thesis"
%%% End: 
